---
title: "Data Processing"
author: "Francis Troy Kirinhakone & Carlos HeHe"
date: "11/12/2018"
output: html_document
---
#Import library and datasets
```{r}
library(tidyverse)
customers = readxl::read_xls(path = "~/GitHub/datasci_proj/brazilian-ecommerce_ver6/olist_customers_dataset.xls")
geolocation = readxl::read_xls(path = "~/GitHub/datasci_proj/brazilian-ecommerce_ver6/olist_geolocation_dataset.xls")
order_items = readxl::read_xls(path = "~/GitHub/datasci_proj/brazilian-ecommerce_ver6/olist_order_items_dataset.xls")
order_payments = readxl::read_xls(path = "~/GitHub/datasci_proj/brazilian-ecommerce_ver6/olist_order_payments_dataset.xls")
order_reviews = readxl::read_xls(path = "~/GitHub/datasci_proj/brazilian-ecommerce_ver6/olist_order_reviews_dataset.xls")
orders = readxl::read_xls(path = "~/GitHub/datasci_proj/brazilian-ecommerce_ver6/olist_orders_dataset.xls")
products = readxl::read_xls(path = "~/GitHub/datasci_proj/brazilian-ecommerce_ver6/olist_products_dataset.xls")
sellers = readxl::read_xls(path = "~/GitHub/datasci_proj/brazilian-ecommerce_ver6/olist_sellers_dataset.xls")
product_category = readxl::read_xls(path = "~/GitHub/datasci_proj/brazilian-ecommerce_ver6/product_category_name_translation.xls")
```

#Description of the attributes of each dataset
```{r}
names(customers)
```
```{r}
names(geolocation)
```
```{r}
names(order_items)
```
```{r}
order_payments %>%
  names()
```
```{r}
order_reviews %>%
  names()
```
```{r}
orders %>% names()
```
```{r}
product_category %>% names()
```
```{r}
products %>% names()
```
```{r}
sellers %>% names()
```

#Exploratory Data Analysis Stage
```{r}
order_items$price %>%
  summary()

order_items %>% arrange(desc(price)) %>%
   select(price, everything()) #place price as the first column
```
We see that there is an outlier at the max of 6735. Maybe we should exclude this point?

#What the correlation between customer_id and price?

Prep the dataframe, temp, to plot.
```{r}
temp = data.frame(customers$customer_unique_id)
temp%>%mutate(customers$customer_id)->temp
temp%>%mutate(order_items$price) -> temp
temp%>%arrange(customers.customer_unique_id)
temp%>%arrange(customers$customer_id)

##find class type
class(temp$customers.customer_unique_id)#factor type...need to convert to string
class(temp$`customers$customer_id`)
class(temp$`order_items$price`)
```
Now use the plot fuction to product a scatter plot(x,y) x = customer_unique_id, y = order_items$price
```{r}
plot(temp$customers.customer_unique_id,temp$`order_items$price`, 
     bty=n,
     col="red",
     main="Customer to Item Price",
     xlab="Customer_Unique_id",
     ylab="Item_Price",
     cex.axis=.5,
     pch=16)
```
Looking at the plot we see there are a few outliers. So we can say that there's a few high end purchases that are infrequent. These points may skew our model and should be exluded.






